\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{green}
\moderncvicons{awesome}

\usepackage[scale=0.80]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3.1cm}
\renewcommand{\baselinestretch}{1.1}

\firstname{Thomas}
\familyname{Eizinger}
\email{thomas@eizinger.io}
\homepage{eizinger.io}
\social[github]{thomaseizinger}
\social[linkedin]{thomas-eizinger}
\social[twitter]{oetzn}
%\photo[90pt][0.4pt]{Portrait} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)

\begin{document}

\makecvtitle

\textit{%
Passionate software engineer with a strong focus on code and software quality.\newline%
I love to share my knowledge through mentoring and talks. %
Always on a hunt for challenges to improve myself.%
}

\vspace{2em}

\section{Work experience}
\cventry{02/2021 -- today}{Tech lead}{CoBloX}{Sydney (Australia)}{full-time}{
    Responsible for translating the company's vision into working software.
    This involves setting the internal team structure, giving guidance on architectural decision and general mentoring of everyone's engineering skills.
    The area of work focuses primarily on non-custodial protocols for building financial products on top of blockchains.
    I have demonstrated self-driven involvement in the open-source communities of libraries and tooling critical to our projects, ensuring fitness for our usecases, most prominently: the Rust language plus tooling, rust-libp2p, rust-bitcoin, rust-elements and monero-rs.
    Additionally to expertise in traditional software engineering, the role requires advanced understanding of cryptography in the field of elliptic curves, f.e. commitment schemes and signature algorithms.
    I am also responsible for the technical interview in the hiring process including evaluation of candidates.
}
\cventry{03/2018 -- 02/2021}{Software Engineer}{CoBloX}{Sydney (Australia)}{full-time}{
    I was involved in the design and development of the COMIT protocol, a peer-to-peer network designed for non-custodial exchange of cryptocurrencies. Work included everything from conceiving network and cryptographic protocols, to frontend work, API design and coaching colleagues on writing idiomatic Rust code.
}
\cventry{10/2017 -- 02/2018}{Software Engineer}{Willhaben.at}{Vienna (Austria)}{full-time}{
    Primarily responsible for maintenance and extension of the core Java codebase. My biggest contribution was a self-driven effort of designing WHML (Willhaben Markup language) - a declarative, domain-specific language for UIs that achieved a consistent and easily maintainable implementation of dynamic forms across multiple platforms. Notable technologies include: Spring Boot, Tomcat, Cybase and Postgres.
}
\cventry{09/2015 -- 06/2017}{Software Engineer}{Senacor Technologies AG}{Vienna (Austria)}{part-time}{
    Responsible for the development of a sales frontend for a major Austrian bank. Notable technologies include: JSF, JPA, EJB, JBoss, Oracle, Java 8, Gradle, Jenkins and Git.
}
\cventry{07/2014 -- 06/2015}{Intern}{IBM Softwaregroup Wien}{Vienna (Austria)}{part-time}{
    Responsible for configuration of standard software as well as development of plugins at various client sites. Notable technologies include: IBM Content Navigator, IBM WebSphere, Spring Boot and DB2.
}
\cventry{01/2014 -- 12/2014}{Software Engineer}{Akademikerhilfe Wien}{Vienna (Austria)}{part-time}{
    Responsible for maintenance and extension of a traffic contingent management software for student dorms. Notable technologies include: PHP, iptables, SNMP and Linux.
}
\cventry{07/2013}{Intern}{T-Mobile Austria E-Business}{Vienna (Austria)}{full-time}{
    Responsible for development of various productivity tools for co-workers. Major contributions include reducing a weekly task from 4 hours to 15 minutes through automation. Notable technologies include: C\texttt{\#}, SQL, Microsoft Excel and WPF
}

\pagebreak

\section{Things I know best}
\cvitem{Languages}{Rust, Java, JavaScript (ES6$+$), C\texttt{\#}, English (IELTS 8/9), German (native)}
\cvitem{Tools}{IntelliJ IDEA (Shortcut expert), Git, *SH}
\cvitem{Concepts}{FP, REST, TDD, Domain Driven Design, APIs, Modelling}

\section{Things I like best}
\cvitem{}{REST (esp. Hypermedia), Open-Source, Cryptography, Design Patterns, DDD, DevOps, Architecture-stuff}

\section{Education}
\cventry{2015 -- 2017}{Master of Science -- Software Engineering}{UAS Technikum Wien}{}{}{Thesis: API-Design in Distributed Systems:~A Comparison between GraphQL and REST\\ \textit{Graduated with distinction}}
\cventry{2012 -- 2015}{Bachelor of Science -- Computer Science}{UAS Technikum Wien}{}{}{Thesis: Documentation of RESTful Web Services Built in Java\\ \textit{Graduated with distinction}}
\cventry{2003 -- 2011}{Secondary school}{BRG Schloss Wagrain V\"ocklabruck, Upper Austria}{}{}{}

\section{Side jobs \& freelancer projects}
\cventry{WS 2017}{Professor}{UAS Technikum Wien}{}{}{Lecture: Single Page Applications in JavaScript -- 1.5 ECTS}
\cventry{02/2015 -- 06/2017}{Tutor}{UAS Technikum Wien}{}{}{C, C\texttt{++}, Java, C\texttt{\#}, Design Patterns, Testing}
\cventry{11/2014 -- 02/2015}{FMVEA-Tool}{Austrian Institute of Technology}{}{}{\textbf{F}ailure \textbf{M}odes, \textbf{V}$\!$ulnerabilities and \textbf{E}ffects \textbf{A}nalysis\newline Technologies: AngularJS, C\texttt{\#}}
\cventry{11/2014 -- 02/2015}{LiveEOG}{UAS Technikum Wien}{}{}{Prototype for controlling a PC using an Electrooculograph (EOG)\newline Technologies: C\texttt{\#}, WPF}
\cventry{10/2012 -- 11/2013}{Tutor}{Huemer Sch\"ulerhilfe Wien}{}{}{Mathematics}

\section{Side projects}
\cventry{since 05/2018}{Curriculum vitae continuous deployment}{}{}{}{As a fun exercise and to ease changes to my CV, I version its TeX source files on GitHub and automatically deploy all changes to my website: \url{github.com/thomaseizinger/curriculum-vitae}}
\cventry{since 03/2016}{nobt.io}{Open-Source Project (\url{github.com/nobt-io})}{}{}{Split your bills with ease\newline Technologies: ReactJS, Redux, Java, AWS}

\section{Talks}
\cventry{Scaling Bitcoin \\ Tokyo 2018}{The State of Atomic Swaps}{Thomas Eizinger}{}{}{Recording: \url{https://youtu.be/FI9cwksTrQs?t=1022}}
\cventry{VoxxedDays \\ Vienna 2018}{Flux: A modern way of doing MVC?}{David Leitner \& Thomas Eizinger}{}{}{Recording: \url{https://youtu.be/h9SDuTSy7ps}}

\end{document}
